---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# saeHB.spatial

<!-- badges: start -->
<!-- badges: end -->

Provides several functions and datasets for area level of Small Area Estimation under Spatial SAR Model using Hierarchical Bayesian (HB) Method. Model-based estimators include the HB estimators based on a Spatial Fay-Herriot model with univariate normal distribution for variable of interest.The 'rjags' package is employed to obtain parameter estimates. For the reference, see Rao and Molina (2015) <doi:10.1002/9781118735855>.

## Author
Arina Mana Sikana, Azka Ubaidillah

## Maintaner
Arina Mana Sikana <221810195@stis.ac.id>

## Function

* `spatial.normal()` This function gives small area estimator under Spatial SAR Model and is implemented to variable of interest (y) that assumed to be a Normal Distribution. The range of data is (-∞ < y < ∞)

## Installation

You can install the development version of `saeHB.spatial` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("arinams/saeHB.spatial")
```

## Example

This is a basic example of using `spatial.normal()` function to make an estimate based on synthetic data in this package

```{r example}
library(saeHB.spatial)

## For data without any non-sampled area
data(sp.norm)       # Load dataset
data(prox.mat)      # Load proximity Matrix

## For data with non-sampled area use sp.normNs

## Fitting model
result <- spatial.normal(y ~ x1 + x2, "vardir", prox.mat, data = sp.norm)

```

Small Area mean Estimates

```r
result$Est
```

Estimated model coefficient

```r
result$coefficient
```

Estimated random effect variances

```{r}
result$refVar
```


## References

* Rao, J.N.K & Molina. (2015). Small Area Estimation 2nd Edition. New Jersey: John Wiley and Sons, Inc. <doi:10.1002/9781118735855>.
* J. Kubacki and A. Jedrzejczak. (2016). Small Area Estimation of Income Under Spatial SAR Model. Statistics in Transition New Series, Vol. 17, No. 3, pp. 365–390. <doi: 10.21307/stattrans-2016-028>.
* H. C. Chung and G. S. Datta. (2020). Bayesian Hierarchical Spatial Models for Small Area Estimation. Research Report Series. Washington, D.C.: U.S. Census Bureau.
